Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-03-12 Paper.tex
merge definitions of the SNARKV contract

\begin{eqnarray}
\Xi_{\mathtt{EXPMOD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:} \\
g_{\mathrm{r}} &=& \left\lfloor\frac{f\big(\max(\ell_{M},\ell_{B})\big)\max(\ell'_{E},1)}{G_{quaddivisor}}\right\rfloor \\
f(x) &\equiv& \begin{cases}
x^2 & \text{if}\ x \le 64 \\[0.5em]
\left\lfloor\dfrac{x^2}{4}\right\rfloor + 96 x - 3072 & \text{if}\ 64 < x \le 1024 \\[1em]
\left\lfloor\dfrac{x^2}{16}\right\rfloor + 480x - 199680 & \text{otherwise}
\end{cases}\\
\ell'_{E} &=& \begin{cases}
0 & \text{if}\ \ell_{E}\le 32\wedge E=0 \\
\lfloor \log_2(E)\rfloor &\text{if}\ \ell_{E}\le 32 \wedge E \neq 0 \\
8(\ell_{E} - 32) + \lfloor \log_2(i[(96+\ell_{B})..(127+\ell_{B})]) \rfloor & \text{if}\ 32 < \ell_{E} \wedge i[(96 + \ell_{B})..(127 + \ell_{B})]\neq 0 \\
8(\ell_{E} - 32) & \text{otherwise} \\
\end{cases} \\
\mathbf o &=& \left(B^E\bmod M\right)\in\mathbb P_{8\ell_{M}} \\
\ell_{B} &\equiv& i[0..31] \\
\ell_{E} &\equiv& i[32..63] \\
\ell_{M} &\equiv& i[64..95] \\
B &\equiv& i[96..(95+\ell_{B})] \\
E &\equiv& i[(96+\ell_{B})..(95+\ell_{B}+\ell_{E})] \\
M &\equiv& i[(96+\ell_{B}+\ell_{E})..(95+\ell_{B}+\ell_{E}+\ell_{M})] \\
i[x] &\equiv& \begin{cases}
I_{\mathbf d}[x] &\text{if}\ x < |I_{\mathbf d}| \\
0 &\text{otherwise}
\end{cases}
\end{eqnarray}

@@

Let $G_T$ be the multiplicative abelian group underlying $F_{p^{12}}$. It is known that a non-degenerate bilinear map $e : G_1\times G_2 \to G_T$ exists.
This bilinear map is a type three pairing. The ZK-Snark verification contract takes a set of points $a_i$ that are in $G_1$, and a set of points $b_i$ that are in $G_2$. It checks that
\begin{equation}
\prod_{i=0}^{n}e\left(a_i, b_i\right) = 1
\end{equation}
If this is true, the contract returns $1$, otherwise it returns $0$, unless any of the points $a_i$ or $b_i$ are not on their respective curves, in which case the transaction is reverted.

A 32 byte number $\mathbf{x}\in\mathbf{P}_{256}$ might and might not represent an element of $F_{\mathrm{p}}$.
\begin{equation}
\delta_{\mathrm{p}}(\mathbf x)\equiv\begin{cases}
\mathbf x&\text{if}\ \mathbf x<p\\
\varnothing&\text{otherwise}
\end{cases}
\end{equation}

A 64 byte data $\mathbf x\in\mathbf B_{512}$ might and might not represent an element of $G_1$.
\begin{eqnarray}
\delta_1(\mathbf x)&\equiv&\begin{cases}
g_1&\text{if}\ g_1\in G_1\\
\varnothing&\text{otherwise}
\end{cases}\\
g_1&\equiv&\begin{cases}
(x,y)&\text{if}\ x\neq\varnothing\wedge y\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x&\equiv&\delta_{\mathrm{p}}(\mathbf x[0..31])\\
y&\equiv&\delta_{\mathrm{p}}(\mathbf x[32..63])
\end{eqnarray}

A 128 byte data $\mathbf x\in\mathbf B_{1024}$ might and might not represent an element of $G_2$.
\begin{eqnarray}
\delta_2(\mathbf x)&\equiv&\begin{cases}
g_2&\text{if}\ g_2\in G_2\\
\varnothing&\text{otherwise}
\end{cases}\\
g_2&\equiv&\begin{cases}
((x_0i+y_0),(x_1i+y_1))&\text{if}\ x_0\neq\varnothing\wedge y_0\neq\varnothing\wedge x_1\neq\varnothing\wedge y_1\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x_0&\equiv&\delta_{\mathrm{p}}(\mathbf x[0..31])\\
y_0&\equiv&\delta_{\mathrm{p}}(\mathbf x[32..63])\\
x_1&\equiv&\delta_{\mathrm{p}}(\mathbf x[64..95])\\
y_1&\equiv&\delta_{\mathrm{p}}(\mathbf x[96..127])
\end{eqnarray}

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf o&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1\left(\bar I_{\mathbf d}[0..63]\right)\\
y&\equiv&\delta_1\left(\bar I_{\mathbf d}[64..127]\right)\\
\label{eq:complemented_input}\bar I_{\mathbf d}[x]&\equiv&\begin{cases}
I_{\mathbf d}[x]&\text{if}\ x < |I_{\mathbf d}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf d}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf o&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf d}[0..31]\\
x&\equiv&\delta_1\left(\bar I_{\mathbf d}[32..95]\right)
\end{eqnarray}

>>>>

\begin{eqnarray}
\Xi_{\mathtt{EXPMOD}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{except:} \\
g_{\mathrm{r}} &=& \left\lfloor\frac{f\big(\max(\ell_{M},\ell_{B})\big)\max(\ell'_{E},1)}{G_{quaddivisor}}\right\rfloor \\
f(x) &\equiv& \begin{cases}
x^2 & \text{if}\ x \le 64 \\[0.5em]
\left\lfloor\dfrac{x^2}{4}\right\rfloor + 96 x - 3072 & \text{if}\ 64 < x \le 1024 \\[1em]
\left\lfloor\dfrac{x^2}{16}\right\rfloor + 480x - 199680 & \text{otherwise}
\end{cases}\\
\ell'_{E} &=& \begin{cases}
0 & \text{if}\ \ell_{E}\le 32\wedge E=0 \\
\lfloor \log_2(E)\rfloor &\text{if}\ \ell_{E}\le 32 \wedge E \neq 0 \\
8(\ell_{E} - 32) + \lfloor \log_2(i[(96+\ell_{B})..(127+\ell_{B})]) \rfloor & \text{if}\ 32 < \ell_{E} \wedge i[(96 + \ell_{B})..(127 + \ell_{B})]\neq 0 \\
8(\ell_{E} - 32) & \text{otherwise} \\
\end{cases} \\
\mathbf{o} &=& \left(B^E\bmod M\right)\in\mathbb{P}_{8\ell_{M}} \\
\ell_{B} &\equiv& i[0..31] \\
\ell_{E} &\equiv& i[32..63] \\
\ell_{M} &\equiv& i[64..95] \\
B &\equiv& i[96..(95+\ell_{B})] \\
E &\equiv& i[(96+\ell_{B})..(95+\ell_{B}+\ell_{E})] \\
M &\equiv& i[(96+\ell_{B}+\ell_{E})..(95+\ell_{B}+\ell_{E}+\ell_{M})] \\
i[x] &\equiv& \begin{cases}
I_{\mathbf{d}}[x] &\text{if}\ x < |I_{\mathbf{d}}| \\
0 &\text{otherwise}
\end{cases}
\end{eqnarray}

@@

A 32 byte number $\mathbf{x}\in\mathbf{P}_{256}$ might and might not represent an element of $F_{\mathrm{p}}$.
\begin{equation}
\delta_{\mathrm{p}}(\mathbf{x})\equiv\begin{cases}
\mathbf{x}&\text{if}\ \mathbf{x}<p\\
\varnothing&\text{otherwise}
\end{cases}
\end{equation}

A 64 byte data $\mathbf{x}\in\mathbf{B}_{512}$ might and might not represent an element of $G_1$.
\begin{eqnarray}
\delta_1(\mathbf{x})&\equiv&\begin{cases}
g_1&\text{if}\ g_1\in G_1\\
\varnothing&\text{otherwise}
\end{cases}\\
g_1&\equiv&\begin{cases}
(x,y)&\text{if}\ x\neq\varnothing\wedge y\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[0..31])\\
y&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[32..63])
\end{eqnarray}

A 128 byte data $\mathbf{x}\in\mathbf{B}_{1024}$ might and might not represent an element of $G_2$.
\begin{eqnarray}
\delta_2(\mathbf{x})&\equiv&\begin{cases}
g_2&\text{if}\ g_2\in G_2\\
\varnothing&\text{otherwise}
\end{cases}\\
g_2&\equiv&\begin{cases}
((x_0i+y_0),(x_1i+y_1))&\text{if}\ x_0\neq\varnothing\wedge y_0\neq\varnothing\wedge x_1\neq\varnothing\wedge y_1\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x_0&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[0..31])\\
y_0&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[32..63])\\
x_1&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[64..95])\\
y_1&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[96..127])
\end{eqnarray}

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf{o}[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf{d}}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf{d}}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf{d}}[(|I_{\mathbf{d}}|-192)..(|I_{\mathbf{d}}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf{d}}[(|I_{\mathbf{d}}|-128)..(|I_{\mathbf{d}}|-1)])
\end{eqnarray}

@@

\begin{eqnarray}
\Xi_{\mathtt{BN\_ADD}}&\equiv&\Xi_{\mathtt{BN\_PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_ADD}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\vee y=\varnothing\\
g_{\mathrm{r}} &=& 500\\
\mathbf{o}&\equiv&\delta_1^{-1}(x+y)\quad\text{where $+$ is the group operation in $G_1$}\\
x&\equiv&\delta_1\left(\bar I_{\mathbf{d}}[0..63]\right)\\
y&\equiv&\delta_1\left(\bar I_{\mathbf{d}}[64..127]\right)\\
\label{eq:complemented_input}\bar I_{\mathbf{d}}[x]&\equiv&\begin{cases}
I_{\mathbf{d}}[x]&\text{if}\ x < |I_{\mathbf{d}}|\\
0&\text{otherwise}
\end{cases}
\end{eqnarray}

We define a precompiled contract for scalar multiplication on $G_1$, where $\bar I_{\mathbf{d}}$ is defined in (\ref{eq:complemented_input}).
\begin{eqnarray}
\Xi_{\mathtt{BN\_MUL}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\Xi_{\mathtt{BN\_MUL}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ x=\varnothing\\
g_{\mathrm{r}} &=& 40000\\
\mathbf{o}&\equiv&\delta_1^{-1}(n\cdot x)\quad\text{where $\cdot$ is the scalar multiplication in $G_1$}\\
n&\equiv&\bar I_{\mathbf{d}}[0..31]\\
x&\equiv&\delta_1\left(\bar I_{\mathbf{d}}[32..95]\right)
\end{eqnarray}
